Training a Gaming Agent on Brainwaves

### 2020-08-23 ErrP.tex
Add minor format change to paper
Subo los cambios tomando las modificaciones que subió Natalia.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game. An agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

In this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.  The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated as for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.

@@

This phase is divided into a sequence of run sessions and a gaming agent training match.  During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of a randomly selecting a movement, to reduce deadlocks and loops.  Following the run session, the agent performs a single gaming agent training match.  The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.  For the agent to learn from the feedback generated by the OHC, the next step, given a current state, will be determined by the agent's actions taken from one brainwave session match. This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.  The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

@@

Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using the five different classification algorithms using a 10-fold cross-validation procedure.  The best overall performance is obtained using Logistic Regression.  In addition, the classification accuracy obtained averaging 5 epochs is shown as well.  Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, only producing a clear improvement for the OHCs that contain more samples (1, 3 and 7).

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
\end{subfigure}
\caption{Heatmap for the transfer learning experiment.  }
\label{fig:transferlearning}
\end{figure}

@@

This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic. Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates enhancing the performance of the gaming agent.

One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.  The obtained accuracy to discriminate ErrPs is low.  However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.  Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity. On the other hand, the percentage of false negatives is generally higher.  However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning. \textit{Even when scarce, accurate rewards are very useful for the RL algorithm}.
%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.

@@

At the same time, effective agent training depends on the OHC's training data. Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC.  Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.  There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game. The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.  The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.

@@

This phase is divided into a sequence of run sessions and a gaming agent training match.  During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of a randomly selecting a movement, to reduce deadlocks and loops.  Following the run session, the agent performs a single gaming agent training match.  The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.  For the agent to learn from the feedback generated by the OHC movement actions are determined by the agent's actions that are taken from one brainwave session match. This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.  The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

@@

Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.  The best overall performance is obtained using Logistic Regression.  In addition, the classification accuracy obtained averaging 5 epochs is shown as well.  Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
\end{subfigure}
\caption{Heatmap for the transfer learning experiment. Values represent the reduction in the average number of steps required to reach the goal.  Negative values represent net improvements.}
\label{fig:transferlearning}
\end{figure}

@@

This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic. Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates, enhancing the performance of the gaming agent.

One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.  The obtained accuracy to discriminate ErrPs is low.  However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.  Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity. On the other hand, the percentage of false negatives is generally higher.  However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning. Though scarce, accurate rewards are very useful for the RL algorithm.
%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.

@@

At the same time, effective agent training depends on the OHC's training data. Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC does not increases the performance of the agent.  Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.  There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.
